% ==================== REFERENCES ====================
\begin{thebibliography}{99}

\item[] \textbf{\large الكتب}

\bibitem{dabit2019}
N. Dabit, \textit{React Native in Action}. Shelter Island, NY, USA: Manning Publications, 2019.

\bibitem{masiello2017}
E. Masiello and J. Friedmann, \textit{Mastering React Native}. Birmingham, UK: Packt Publishing, 2017.

\bibitem{casciaro2020}
M. Casciaro and L. Mammino, \textit{Node.js Design Patterns}, 3rd ed. Birmingham, UK: Packt Publishing, 2020.

\item[] \textbf{\large الأوراق العلمية والمجلات الأكاديمية}

\bibitem{wobbrock2009}
J. O. Wobbrock, M. R. Morris, and A. D. Wilson, ``User-defined gestures for surface computing,'' in \textit{Proc. CHI Conference on Human Factors in Computing Systems}, 2009, pp. 1083--1092.

\bibitem{liu2019}
J. Liu, Z. Zhong, J. Wickramasuriya, and V. Vasudevan, ``uWave: Accelerometer-based personalized gesture recognition and its applications,'' \textit{Pervasive and Mobile Computing}, vol. 5, no. 6, pp. 657--675, 2009.

\item[] \textbf{\large مجموعات البيانات والمصادر التقنية}

\item[] \textbf{\large التوثيق والشفرات المصدرية}

\bibitem{npm-docs}
npm, Inc. (2024). \textit{npm Official Documentation: Creating and Publishing Scoped Public Packages}. Retrieved from \url{https://docs.npmjs.com/}

\bibitem{rn-docs}
Meta Platforms, Inc. (2024). \textit{React Native Official Documentation: Gesture Responder System}. Retrieved from \url{https://reactnative.dev/docs/gesture-responder-system}

\bibitem{rngh-docs}
Software Mansion. (2024). \textit{React Native Gesture Handler Documentation}. Retrieved from \url{https://docs.swmansion.com/react-native-gesture-handler/}

\bibitem{reanimated-docs}
Software Mansion. (2024). \textit{React Native Reanimated Documentation: Shared Values and UI Thread}. Retrieved from \url{https://docs.swmansion.com/react-native-reanimated/}

\end{thebibliography}
